# Additional topics

## Regular expressions

### Introduction to `stringi` package 

I recommed to use either `stringr` or `stringi` package in order to process strings and extract characters with regular expression. In this chapter I will show how to use latter.

Please note that a comprehensive description of the `stringi` package can be found in Marek Gągolewski's Programowanie w R book, chapter 10. Currently there is no tutorial in English


### Basic notation

In regular expression w use metacharacters:

+ `\` -- start escape characters
+ `|` -- denotes OR
+ `(` and `)` -- group denotation
+ `[` and `]` -- 
+ `{` and `}` -- specify number of occurences
+ `^` -- starts a specific character
+ `$` -- end with a specific character
+ `*` -- 
+ `+` -- one or more time
+ `?` -- 0 or more times

In addition to above we have

+ `[:alnum:]` -- Alphanumeric characters: [:alpha:] and [:digit:].
+ `[:alpha:]` -- Alphabetic characters: [:lower:] and [:upper:].
+ `[:blank:]` -- Blank characters: space and tab, and possibly other locale-dependent characters such as non-breaking space.
+ `[:cntrl:]` -- Control characters. In ASCII, these characters have octal codes 000 through 037, and 177 (DEL). In another character set, these are the equivalent characters, if any.
+ `[:digit:]` -- Digits: 0 1 2 3 4 5 6 7 8 9.
+ `[:graph:]` -- Graphical characters: [:alnum:] and [:punct:].
+ `[:lower:]` -- Lower-case letters in the current locale.
+ `[:print:]` -- Printable characters: [:alnum:], [:punct:] and space.
+ `[:punct:]` -- Punctuation characters: `! " # $ % & ' ( ) * + , - . / : ; < = > ? @ [ \ ] ^ _ ` { | } ~`.
+ `[:space:]` --  Space characters: tab, newline, vertical tab, form feed, carriage return, space and possibly other locale-dependent characters.
+ `[:upper:]` -- Upper-case letters in the current locale.
+ `[:xdigit:]` -- Hexadecimal digits: `0 1 2 3 4 5 6 7 8 9 A B C D E F a b c d e`


## Examples



Let assume, that we have the following sentence

```
This property has 44.52 m2, 3 rooms and costs 150 430 PLN.
```


```{r}
string <- 'This property has 44.52 m2, 3 rooms and costs 150 430 PLN.'
```


### Extract digits


```{r}
stri_extract(str = string,
             regex = '[:digit:]')

## the same as  stri_extract(str = string, regex = '\\d')


```


```{r}
stri_extract(str = string,
             regex = '[:digit:]',
             mode = 'all')

## the same as  stri_extract(str = string, regex = '\\d', mode = 'all')
## we will use \\d notatio  hereinafter
```

We can add `+` to indicate that we are interested in extracting one or more digit

```{r}
stri_extract(str = string, regex = '\\d+', mode = 'all')
```

Now, we are interested in extrating number of rooms. For that we will use word `rooms`.

```{r}
stri_extract(str = string, regex = '\\d rooms', mode = 'all')
stri_extract(str = string, regex = '\\d{1,2} rooms', mode = 'all') ## we specify that only digits from one to two digits will be present
```

This result can be further processed but we will leave this for your own excercise.

Now, we will follow to extract floor area. 

```{r}
stri_extract(str = string, regex = '\\d{1,3}\\.\\d{1,2} m2', mode = 'all')
```

When this will work?

```{r}
stri_extract(str = c('24.23 m2','55 m2', '124.53 m2'), 
             regex = '\\d{1,3}\\.\\d{1,2} m2', 
             mode = 'all')
```

The second argument was not extracted. What should we do in this case? How to modify this code?

```{r}
stri_extract(str = c('24.23 m2','55 m2', '124.53 m2'), 
             regex = '\\d{1,3}(\\.\\d{1,2})? m2', 
             mode = 'all')
```

Next we just need to remove m2 or we need to take into account that m2 will not be taken into account during extraction.


